---
title: "[Regression App](https://tevgeniou.github.io/RegressionApp/)"
author: "[T. Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), INSEAD"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    theme: paper
runtime: shiny
---

`r knitr::opts_knit$set(progress=FALSE, verbose=FALSE)`

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages({
  library(shiny)
  library(knitr)
  library(c3)
  load("AllDatasets.Rdata")
})  # end suppressPackageStartupMessages

tags$style(type="text/css", "p { text-align:justify; }")
tags$style(type="text/css", # see #96 for details
" @media (min-width: 768px) and (max-width: 991px) {
    .col-sm-8 { width: 82%; }
    .col-sm-4 { width: 18%; }
    div.tocify { width: 16%; }
  }"
)
```

<br>

## Overview

This interactive toolkit can be used to run regression models. A number of datasets are available, however if custom data need to be analysed the source code of the tool should be pulled from the [tool repo](https://github.com/tevgeniou/UDJ) and modified accordingly. 

Regression analysis can be done in different ways. For example

1. Choose dependent and independent variables 
2. Study scatterplots, check for outliers and correlation matrix (also look for Multicollinerarity).
3. Run a first regression.
4. Deal with multicolinearity. 
5. If F-test is not  significant, then do not continue, or return to step 1.
6. Check for significance of coefficients (t-test)
7. Deal with insignificant variables
8. Check regression assumptions using residual analysis
9. Consider nonlinear transformations and other independent variables
9. Use adjusted R-square, as well as intuition, to select among different regressions
10. Interpret, explain, and predict (point and confidence intervals)
11. Check again for outliers and if necessary go back to step 2 or 1

The sections below allow the analysis following such a process. 

## Select Dataset

The following datasets are available for analysis using the web-based tool. 

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

fluidPage(
  # Major markets
  fluidRow(
    column(12, selectInput("datasetused", 
                           "Select the dataset to use",
                           choices= names(all_datasets),
                           selected = "SalesExerciseData",
                           multiple=FALSE, width="100%"))
  )
)

dataset <- reactive({
  all_datasets[[input$datasetused]]
})

```

## Select Variables

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
renderUI({fluidPage(
  fluidRow(
    column(12, selectInput("dependentvar", 
                           "Select the Dependent Variable to use",
                           choices= colnames(dataset()),
                           selected = "SALES",
                           multiple=FALSE, width="100%"))
  )
)
})

renderUI({fluidPage(
  fluidRow(
    column(12, selectizeInput("independentvar", 
                              "Select the Independent Variables to use",
                              choices= setdiff(colnames(dataset()),input$dependentvar),
                              selected = setdiff(colnames(dataset()),input$dependentvar),
                              multiple=TRUE, width="100%",
                              options=list(plugins=c("remove_button","drag_drop"))))
  )
)
})
```


## Study Scatterplots

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
renderUI({fluidPage(
  fluidRow(
    column(6, selectInput("scatter1", 
                           "Select the x-axis Variable",
                           choices= colnames(dataset()),
                           selected = colnames(dataset())[1],
                           multiple=FALSE, width="100%")),
    column(6, selectInput("scatter2", 
                           "Select the y-axis Variable",
                           choices= colnames(dataset()),
                           selected = colnames(dataset())[2],
                           multiple=FALSE, width="100%"))
    
  )
)
})


tags$div(style='height:480px', renderC3({
  shiny::validate(
    need(input$scatter1, message=FALSE),
    need(input$scatter2, message=FALSE)
  )
  scatter1 <- input$scatter1
  scatter2 <- input$scatter2
  dataset <- isolate(dataset())
  c3(cbind.data.frame(x=dataset[[scatter1]],y=dataset[[scatter2]]), x="x", y="y") %>%
    c3_scatter() %>%
    xAxis(label=scatter1) %>% 
    yAxis(label=scatter2) %>%
    legend(hide="y")
}))

```

## Study Correlation

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
renderTable({
  shiny::validate(
    need(input$dependentvar, message=FALSE),
    need(input$independentvar, message=FALSE)
  )
  dependentvar <- input$dependentvar
  independentvar <- input$independentvar
  dataset <- isolate(dataset())
  cor(dataset[,c(dependentvar,independentvar)])
})

```


## Regression Output

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
the_regression_output <- reactive({
  shiny::validate(
    need(input$dependentvar, message=FALSE),
    need(input$independentvar, message=FALSE)
  )
  dependentvar <- input$dependentvar
  independentvar <- input$independentvar
  dataset <- isolate(dataset())
  regression_model = as.formula(paste(dependentvar, " ~ ",paste(independentvar,collapse = "+"), sep=""))
  the_fit<-lm(regression_model,data=dataset)      
  
  print_the_fit<-as.list(summary(the_fit))
  the_res= c(
    print_the_fit$r.squared,
    print_the_fit$adj.r.squared,
    print_the_fit$fstatistic["value"],
    pf(
      print_the_fit$fstatistic[1],
      print_the_fit$fstatistic[2],
      print_the_fit$fstatistic[3],
      lower.tail = FALSE
    ),
    sqrt(deviance(the_fit)/df.residual(the_fit)),
    the_fit$df
  )
  the_res = as.matrix(the_res,ncol=1)
  rownames(the_res)<-c("R square","Adjusted R Square", "F-statistic", "p-value",
                       "Residual standard error","degrees of freedom")
  colnames(the_res)<-"Values"
  the_res = as.data.frame(the_res)
  list(
    the_fit=the_fit,
     the_res = the_res
  )
})

renderPrint({
  the_fit_all = the_regression_output()
  summary(the_fit_all$the_fit)
})

```

## Residual Analysis

### Plot of the Residuals
```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
the_residuals_plot_tab<-reactive({
  the_fit = the_regression_output()    
  residuals(the_fit$the_fit)       
})

tags$div(style='height:480px', renderC3({
  y <- the_residuals_plot_tab()
  c3(data.frame(x=1:length(y), y=y), x="x", y="y") %>%
    c3_scatter() %>%
    xAxis(label="Observations") %>% 
    yAxis(label="Residuals") %>%
    legend(hide="y")
}))
```


### Residuals Histogram
```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

tags$div(style='height:480px', renderC3({    
  x <- the_residuals_plot_tab()
  h <- hist(x, breaks=max(5, round(length(x)/5)), plot=FALSE)
  df <- data.frame(x=head(h$breaks, -1), Frequency=h$counts)
  c3(df, x="x", y="Frequency") %>%
    c3_bar()
}))

```

### Residuals Scatterplots

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
renderUI({fluidPage(
  fluidRow(
    column(12, selectInput("resscatter1", 
                           "Select the Variable to plot against the residuals",
                           choices= colnames(dataset()),
                           selected = colnames(dataset())[1],
                           multiple=FALSE, width="100%"))
  )
)
})



tags$div(style='height:480px', renderC3({
  shiny::validate(
    need(input$resscatter1, message=FALSE)
  )
  resscatter1 <- input$resscatter1
  dataset <- isolate(dataset())
  c3(cbind.data.frame(x=dataset[[resscatter1]],y=the_residuals_plot_tab()), x="x", y="y") %>%
    c3_scatter() %>%
    xAxis(label=resscatter1) %>% 
    yAxis(label="Residuals") %>%
    legend(hide="y")
}))

```

<hr>

<div style="height: 450px;" class="tocify-extend-page" data-unique="tocify-extend-page">
</div>

<script>
$(document).ready(function() {
    console.log("Initializing 'selectize-control' patch...");
    setTimeout(function() {
        console.log("Applying 'selectize-control' patch...");
        $(".selectize-control").addClass("single");
    }, 1000);
});
</script>
