---
title: "[Regression App](https://tevgeniou.github.io/RegressionApp/)"
author: "[INSEAD Decision Sciences](https://www.insead.edu/faculty-research/academic-areas/decision-sciences)"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    theme: paper
runtime: shiny_prerendered
---

`r knitr::opts_knit$set(progress=FALSE, verbose=FALSE)`

```{r context="setup", echo=FALSE}
suppressPackageStartupMessages({
  library(shiny)
  library(knitr)
  library(openxlsx)
  library(stats)
  library(c3)           # devtools::install_github("mrjoh3/c3")
  library(formattable)  # devtools::install_github("vkapartzianis/formattable")
  load("AllDatasets.Rdata")
})  # end suppressPackageStartupMessages

tags$style(type="text/css", "p { text-align:justify; }")
tags$style(type="text/css", # see #96 for details
" @media (min-width: 768px) and (max-width: 991px) {
    .col-sm-8 { width: 82%; }
    .col-sm-4 { width: 18%; }
    div.tocify { width: 16%; }
  }"
)

tags$style(type="text/css", ".c3 svg { font-size:13px; font-family:\"Roboto\", \"Helvetica Neue\", Helvetica, Arial, sans-serif; }")
tags$style(type="text/css", ".formattable_widget { overflow:auto; max-height:425px; margin-bottom:23px; }")
tags$style(type="text/css", ".formattable_widget table { margin-bottom:0; }")
tags$style(type="text/css", ".formattable_widget td, .formattable_widget th { white-space: nowrap; }")

opts_chunk$set(echo=FALSE)

html.summary.lm <- function (x, digits = max(3L, getOption("digits") - 3L), ...) {
  tag.list <- list()
  tag.print <- function(...) tag.list <<- c(tag.list, tagList(...))
  tag.table <- function(x, ...) tag.print(tags$div(class="formattable_widget", HTML(kable(as.data.frame(x), format="html", table.attr = "class='table'", ...))))
  
# tag.print(
#   tags$h4("Call:"),
#   tags$pre(paste(deparse(x$call), sep="\n", collapse = "\n")),
#   tags$br()
# )
  
# resid <- x$residuals
  df <- x$df
  rdf <- df[2L]
# tag.print(tags$h4(paste0(
#   if(!is.null(x$weights) && diff(range(x$weights))) "Weighted ",
#   "Residuals:"
# )))
# if (rdf > 5L) {
#   nam <- c("Min", "1Q", "Median", "3Q", "Max")
#   rq <- if (length(dim(resid)) == 2L) {
#     structure(apply(t(resid), 1L, quantile),
#       dimnames = list(nam, dimnames(resid)[[2L]]))
#   } else  {
#     zz <- zapsmall(quantile(resid), digits + 1L)
#     structure(zz, names = nam)
#   }
#   tag.table(t(rq), digits = digits, ...)
# } else if (rdf > 0L) {
#   tag.table(t(resid), digits = digits, ...)
# } else { # rdf == 0 : perfect fit!
#   tag.print(paste("ALL", df[1L], "residuals are 0: no residual degrees of freedom!"))
# }
  
  tag.print(tags$h4("Coefficients:"))
  if (length(x$aliased) == 0L) {
    tag.print("No Coefficients")
  } else {
    if (nsingular <- df[3L] - df[1L]) {
      tag.print(paste0("(", nsingular, " not defined because of singularities)"))
    }
    coefs <- x$coefficients
    if(any(aliased <- x$aliased)) {
      cn <- names(aliased)
      coefs <- matrix(NA, length(aliased), 4, dimnames=list(cn, colnames(coefs)))
      coefs[!aliased, ] <- x$coefficients
    }
    # TODO: handle `Signif` computation errors and NAs in `coefs`
    nc <- ncol(coefs)
    xm <- data.matrix(coefs)
    pv <- as.vector(xm[, nc]) # drop names
    Signif <- symnum(pv, corr = FALSE, na = FALSE,
#                    cutpoints = c(0,  .001,.01,.05, .1, 1),
#                    symbols   =  c("***","**","*","."," "))
                     cutpoints = c(0, .01, .05, .1,  1),
                     symbols   = c("**", "*", "+", " "))
    Cf <- cbind.data.frame(coefs, Signif=format(Signif))
    tag.table(Cf, digits=digits)
    tag.print(tags$div(style="margin-top:-10px; margin-bottom:20px;", 
      "Signif. codes:", 
      tags$pre(attr(Signif,"legend"))
    ))
  }

  tag.print(tags$h4("Statistics:"))
  tag.print(
    tags$b("Residual standard error:"),
    paste(format(signif(x$sigma, digits)), "on", rdf, "degrees of freedom")
  )
  if (nzchar(mess <- naprint(x$na.action))) {
    tag.print(paste0("  (",mess, ")"))
  }
  if (!is.null(x$fstatistic)) {
    tag.print(
      tags$br(),
      tags$b("Multiple R-squared:"), 
      formatC(x$r.squared, digits=digits),
      tags$b("Adjusted R-squared:"), 
      formatC(x$adj.r.squared, digits=digits),
      tags$b("F-statistic:"), 
      paste(formatC(x$fstatistic[1L], digits = digits), "on", x$fstatistic[2L], "and", x$fstatistic[3L], "DF"),
      tags$b("p-value:"), 
      format.pval(pf(x$fstatistic[1L], x$fstatistic[2L], x$fstatistic[3L], lower.tail=FALSE), digits=digits)
    )
  }
  tag.print(tags$br())
  
  tag.list
}
```

<br>

## Dataset

The following datasets are readily available for analysis. You can specify a custom dataset, by choosing "Custom..." and uploading your data file (in .CSV or .XLSX format).

```{r context="render"}
# Major markets
fluidRow(column(12, 
  selectInput("datasetused", 
              "Select the dataset to use:",
              choices = c("[Custom...]", names(all_datasets)),
              selected = "SalesExerciseData",
              multiple=FALSE, width="100%")
))
conditionalPanel("input.datasetused=='[Custom...]'", fluidRow(column(12,
  fileInput("dataFile", "Upload a custom dataset:",
            # http://stackoverflow.com/questions/11832930/html-input-file-accept-attribute-file-type-csv
            accept = (".csv,application/vnd.openxmlformats-officedocument.spreadsheetml.sheet"),
            width = "100%")
)))
```

```{r context="server"}
dataset <- reactive({
  datasetused <- input$datasetused
  if (datasetused != "[Custom...]") {
    all_datasets[[input$datasetused]]
  } else {
    datapath <- input$dataFile$datapath
    if (is.null(datapath)) {
      
    } else {
      df <- try(read.csv(datapath, stringsAsFactors=FALSE), silent=TRUE)
      df.valid <- class(df) == "data.frame" && any(sapply(df, is.numeric))
      if (!df.valid) {
        df <- try(read.xlsx(datapath), silent=TRUE)
        df.valid <- class(df) == "data.frame" && any(sapply(df, is.numeric))
      }
      if (!df.valid) {
        showModal(modalDialog(title="Error", HTML("The data file contains no valid numeric variables.<br><br>Common problems include a column separator other than the comma (`,`), a decimal point other than the period (`.`) or multiple tables/sheets in Excel documents.")))
        shiny::validate(need(df.valid, message=FALSE))
      }
      if (is.null(rownames(df)) || identical(rownames(df), as.character(1:nrow(df)))) {
        rownames(df) <- paste0("observation ", sprintf("%02i", 1:nrow(df)))
      }
      df
    }
  }
})
```

## Variables

```{r context="render"}
uiOutput("dependentvarUI")
uiOutput("independentvarUI")
```

```{r context="server"}
output$dependentvarUI <- renderUI({fluidRow(column(12, 
  selectInput(
    "dependentvar", 
    "Select the Dependent Variable to use:",
    choices = colnames(dataset()),
    selected = "SALES",
    multiple=FALSE, width="100%"
  )
))})

output$independentvarUI <- renderUI({fluidRow(column(12, 
  selectizeInput(
    "independentvar", 
    "Select the Independent Variables to use:",
    choices = setdiff(colnames(dataset()),input$dependentvar),
    selected = setdiff(colnames(dataset()),input$dependentvar),
    multiple=TRUE, width="100%",
    options=list(plugins=c("remove_button","drag_drop"))
  )
))})
```

## Scatterplots

```{r context="render"}
uiOutput("scatterUI")
tags$div(style='height:600px', c3Output("scatterC3"))
```

```{r context="server"}
output$scatterUI <- renderUI({fluidRow(
  column(6, selectInput(
    "scatter1", 
    "Select the x-axis Variable:",
    choices = colnames(dataset()),
    selected = colnames(dataset())[1],
    multiple=FALSE, width="100%")
  ),
  column(6, selectInput(
    "scatter2", 
    "Select the y-axis Variable:",
    choices = colnames(dataset()),
    selected = colnames(dataset())[2],
    multiple=FALSE, width="100%")
  )
)})

output$scatterC3 <- renderC3({
  shiny::validate(
    need(input$scatter1, message=FALSE),
    need(input$scatter2, message=FALSE)
  )
  scatter1 <- input$scatter1
  scatter2 <- input$scatter2
  dataset <- isolate(dataset())
  c3(cbind.data.frame(x=dataset[[scatter1]],y=dataset[[scatter2]]), x="x", y="y") %>%
    c3_scatter() %>%
    xAxis(label=scatter1) %>% 
    # format y Axis for floating point imprecision, see https://github.com/c3js/c3/issues/797
    yAxis(label=scatter2, tick=list(format=htmlwidgets::JS("d3.format('.3n')"))) %>% # 
    legend(hide="y")
})
```

## Correlations

```{r context="render"}
sliderInput("correlationThreshold", "Select significance threshold:", 0.00, 1.00, 0.20, width="100%")
uiOutput("correlationTable")
```

```{r context="server"}
output$correlationTable <- renderUI({
  shiny::validate(
    need(input$dependentvar, message=FALSE),
    need(input$independentvar, message=FALSE)
  )
  dependentvar <- input$dependentvar
  independentvar <- input$independentvar
  dataset <- isolate(dataset())
  df <- as.data.frame(cor(dataset[,c(dependentvar,independentvar)]))
  df[abs(df) < input$correlationThreshold] <- NA
  
  normalize.abs <- function(x, min=0, max=1, na.rm=FALSE) normalize(abs(x), min, max, na.rm)
  normalize.cor <- function(x, min=0, max=1, na.rm=FALSE) abs(x)
  x <- lapply(colnames(df), function(col) {
    color_bar(rgb(238, 238, 238, max=255), normalize.cor, min=0.1, na.rm=TRUE)
  })
  names(x) <- colnames(df)
  HTML(gsub("NA", "", format_table(df, x, digits=2)))
})
```

## Regression Output

```{r context="render"}
uiOutput("regressionHTML")
```

```{r context="server"}
the_regression_output <- reactive({
  shiny::validate(
    need(input$dependentvar, message=FALSE),
    need(input$independentvar, message=FALSE)
  )
  dependentvar <- input$dependentvar
  independentvar <- input$independentvar
  dataset <- isolate(dataset())
  regression_model = as.formula(paste(dependentvar, " ~ ",paste(independentvar,collapse = "+"), sep=""))
  the_fit<-lm(regression_model,data=dataset)      
  save(the_fit, file="the_fit.RData")
  
  print_the_fit<-as.list(summary(the_fit))
  the_res= c(
    print_the_fit$r.squared,
    print_the_fit$adj.r.squared,
    print_the_fit$fstatistic["value"],
    pf(
      print_the_fit$fstatistic[1],
      print_the_fit$fstatistic[2],
      print_the_fit$fstatistic[3],
      lower.tail = FALSE
    ),
    sqrt(deviance(the_fit)/df.residual(the_fit)),
    the_fit$df
  )
  the_res = as.matrix(the_res,ncol=1)
  rownames(the_res)<-c("R square","Adjusted R Square", "F-statistic", "p-value",
                       "Residual standard error","degrees of freedom")
  colnames(the_res)<-"Values"
  the_res = as.data.frame(the_res)
  list(
    the_fit=the_fit,
     the_res = the_res
  )
})

output$regressionHTML <- renderUI({
  the_fit_all = the_regression_output()
  html.summary.lm(summary(the_fit_all$the_fit))
})
```

## Residual Analysis

### Plot

```{r context="render"}
tags$div(style='height:600px', c3Output("residualsPlot"))
```

```{r context="server"}
the_residuals_plot_tab<-reactive({
  the_fit = the_regression_output()    
  residuals(the_fit$the_fit)       
})

output$residualsPlot <- renderC3({
  y <- the_residuals_plot_tab()
  c3(data.frame(x=1:length(y), y=y), x="x", y="y") %>%
    c3_scatter() %>%
    xAxis(label="Observations") %>% 
    # format y Axis for floating point imprecision, see https://github.com/c3js/c3/issues/797
    yAxis(label="Residuals", tick=list(format=htmlwidgets::JS("d3.format('.3n')"))) %>% # 
    legend(hide="y")
})
```

### Histogram

```{r context="render"}
tags$div(style='height:600px', c3Output("residualsHist"))
```

```{r context="server"}
output$residualsHist <- renderC3({    
  x <- the_residuals_plot_tab()
# h <- hist(x, breaks=max(5, round(length(x)/5)), plot=FALSE)
  h <- hist(x, plot=FALSE)
  df <- data.frame(x=head(h$breaks, -1), Frequency=h$counts)
  c3(df, x="x", y="Frequency") %>%
    c3_bar() %>%
    # format y Axis for floating point imprecision, see https://github.com/c3js/c3/issues/797
    yAxis(label="Frequency", tick=list(format=htmlwidgets::JS("d3.format('.3n')"))) %>% # 
    legend(hide="Frequency")
})
```

### Scatterplots

```{r context="render"}
uiOutput("resscatterUI")
tags$div(style='height:600px', c3Output("resscatterPlot"))
```

```{r context="server"}
output$resscatterUI <- renderUI({fluidRow(column(12,
  selectInput(
    "resscatter1", 
    "Select the Variable to plot against the residuals:",
    choices = colnames(dataset()),
    selected = colnames(dataset())[1],
    multiple=FALSE, width="100%")
  )
)})

output$resscatterPlot <- renderC3({
  shiny::validate(
    need(input$resscatter1, message=FALSE)
  )
  resscatter1 <- input$resscatter1
  dataset <- isolate(dataset())
  c3(cbind.data.frame(x=dataset[[resscatter1]],y=round(the_residuals_plot_tab(),2)), x="x", y="y") %>%
    c3_scatter() %>%
    xAxis(label=resscatter1) %>% 
    # format y Axis for floating point imprecision, see https://github.com/c3js/c3/issues/797
    yAxis(label="Residuals", tick=list(format=htmlwidgets::JS("d3.format('.3n')"))) %>% # 
    legend(hide="y")
})
```

<hr>

<div style="height: 450px;" class="tocify-extend-page" data-unique="tocify-extend-page">
</div>

<script>
$(document).ready(function() {
    console.log("Initializing 'selectize-control' patch...");
    setTimeout(function() {
        console.log("Applying 'selectize-control' patch...");
        $(".selectize-control").addClass("single");
    }, 1000);
});
</script>
