---
title: "[Regression App](https://tevgeniou.github.io/RegressionApp/)"
author: "[INSEAD Decision Sciences](https://www.insead.edu/faculty-research/academic-areas/decision-sciences)"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    theme: paper
runtime: shiny
---

`r knitr::opts_knit$set(progress=FALSE, verbose=FALSE)`

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages({
  library(shiny)
  library(knitr)
  load("AllDatasets.Rdata")
})  # end suppressPackageStartupMessages

tags$style(type="text/css", "p { text-align:justify; }")
tags$style(type="text/css", # see #96 for details
" @media (min-width: 768px) and (max-width: 991px) {
    .col-sm-8 { width: 82%; }
    .col-sm-4 { width: 18%; }
    div.tocify { width: 16%; }
  }"
)
```

<br>

## Dataset


```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

fluidPage(
  # Major markets
  fluidRow(
    column(12, selectInput("datasetused", 
                           "Select the dataset to use",
                           choices= names(all_datasets),
                           selected = "SalesExerciseData",
                           multiple=FALSE, width="100%"))
  )
)

dataset <- reactive({
  all_datasets[[input$datasetused]]
})

```

## Variables

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
renderUI({fluidPage(
  fluidRow(
    column(12, selectInput("dependentvar", 
                           "Select the Dependent Variable to use",
                           choices= colnames(dataset()),
                           selected = "SALES",
                           multiple=FALSE, width="100%"))
  )
)
})

renderUI({fluidPage(
  fluidRow(
    column(12, selectizeInput("independentvar", 
                              "Select the Independent Variables to use",
                              choices= setdiff(colnames(dataset()),input$dependentvar),
                              selected = setdiff(colnames(dataset()),input$dependentvar),
                              multiple=TRUE, width="100%",
                              options=list(plugins=c("remove_button","drag_drop"))))
  )
)
})
```


## Scatterplots

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
renderUI({fluidPage(
  fluidRow(
    column(6, selectInput("scatter1", 
                           "Select the x-axis Variable",
                           choices= colnames(dataset()),
                           selected = colnames(dataset())[1],
                           multiple=FALSE, width="100%")),
    column(6, selectInput("scatter2", 
                           "Select the y-axis Variable",
                           choices= colnames(dataset()),
                           selected = colnames(dataset())[2],
                           multiple=FALSE, width="100%"))
    
  )
)
})


renderPlot({
  validate(
    need(input$scatter1, message=FALSE),
    need(input$scatter2, message=FALSE)
  )
  scatter1 <- input$scatter1
  scatter2 <- input$scatter2
  dataset <- isolate(dataset())
  plot(dataset[[scatter1]],dataset[[scatter2]], xlab=scatter1, ylab=scatter2)
}) 

```

## Correlations

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
renderTable({
  validate(
    need(input$dependentvar, message=FALSE),
    need(input$independentvar, message=FALSE)
  )
  dependentvar <- input$dependentvar
  independentvar <- input$independentvar
  dataset <- isolate(dataset())
  cor(dataset[,c(dependentvar,independentvar)])
})

```


## Regression Output

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
the_regression_output <- reactive({
  validate(
    need(input$dependentvar, message=FALSE),
    need(input$independentvar, message=FALSE)
  )
  dependentvar <- input$dependentvar
  independentvar <- input$independentvar
  dataset <- isolate(dataset())
  regression_model = as.formula(paste(dependentvar, " ~ ",paste(independentvar,collapse = "+"), sep=""))
  the_fit<-lm(regression_model,data=dataset)      
  
  print_the_fit<-as.list(summary(the_fit))
  the_res= c(
    print_the_fit$r.squared,
    print_the_fit$adj.r.squared,
    print_the_fit$fstatistic["value"],
    pf(
      print_the_fit$fstatistic[1],
      print_the_fit$fstatistic[2],
      print_the_fit$fstatistic[3],
      lower.tail = FALSE
    ),
    sqrt(deviance(the_fit)/df.residual(the_fit)),
    the_fit$df
  )
  the_res = as.matrix(the_res,ncol=1)
  rownames(the_res)<-c("R square","Adjusted R Square", "F-statistic", "p-value",
                       "Residual standard error","degrees of freedom")
  colnames(the_res)<-"Values"
  the_res = as.data.frame(the_res)
  list(
    the_fit=the_fit,
     the_res = the_res
  )
})

renderTable({
  the_fit_all = the_regression_output()
  summary(the_fit_all$the_fit)
})

```

## Residual Analysis

### Plot of the Residuals
```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
the_residuals_plot_tab<-reactive({
  the_fit = the_regression_output()    
  residuals(the_fit$the_fit)       
})

renderPlot({    
  plot(the_residuals_plot_tab(),xlab="Observations",ylab="Residuals",main="The Residuals")
})
```


### Residuals Histogram
```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

renderPlot({    
  dataused = the_residuals_plot_tab()
  hist(dataused, main = "Histogram of the Residuals", breaks = max(5,round(length(dataused)/5)))
})

```

### Residuals Scatterplots

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
renderUI({fluidPage(
  fluidRow(
    column(12, selectInput("resscatter1", 
                           "Select the Variable to plot against the residuals",
                           choices= colnames(dataset()),
                           selected = colnames(dataset())[1],
                           multiple=FALSE, width="100%"))
  )
)
})



renderPlot({
  validate(
    need(input$resscatter1, message=FALSE)
  )
  resscatter1 <- input$resscatter1
  dataset <- isolate(dataset())
  plot(dataset[[resscatter1]],the_residuals_plot_tab(),xlab=resscatter1,ylab="Residuals")
})

```

<hr>

<div style="height: 450px;" class="tocify-extend-page" data-unique="tocify-extend-page">
</div>

<script>
$(document).ready(function() {
    console.log("Initializing 'selectize-control' patch...");
    setTimeout(function() {
        console.log("Applying 'selectize-control' patch...");
        $(".selectize-control").addClass("single");
    }, 1000);
});
</script>
